---
title: "CART_bleeding analysis"
author: "Christelle Colin-Leitzinger"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: yes
    toc_float: yes
    toc_collapsed: no
    theme: united
    highlight: pygments
    df_print: paged
editor_options:
  chunk_output_type: console
---

<style type="text/css">
h1.title {
  font-size: 25px;
}
.figure {
   margin-top: 25px;
   margin-bottom: 25px;
}

table {
    margin-top: 25px;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```


<style>
div.blue { background-color:#0099CC; border-radius: 5px; padding: 20px; font-size: 38px}
</style>
<div class = "blue">

<span style="color: white;">CART_bleeding analysis</span>

</div>
<br>

```{r library, include=FALSE}
library(tidyverse)
library(gtsummary)
theme_gtsummary_compact()
theme_set(theme_classic())
```

```{r load}
cart_MM <-
  readxl::read_xlsx(
    "turabData Cleaning v11 11.16.2022.xlsx",
                    # skip = 1, n_max = 198,
    sheet = "Data - Original"
                    ) %>% 
  janitor::clean_names()

summary(MM_cart)
```

```{r}
recoded_cart <- cart_MM %>% 
  # Recoding
  mutate(sex = case_when(
    sex == 0             ~ "Male",
    sex == 1             ~ "Female"
  )) %>% 
  mutate(race = case_when(
    race == 1             ~ "NHW",
    race == 2             ~ "NHB",
    race == 3             ~ "Hipanic",
    race == 4             ~ "Asian",
    race == 5             ~ "Others"
  )) %>% 
  mutate(car_t_product = case_when(
    car_t_product == 1             ~ "Abecma",
    car_t_product == 2             ~ "cilta-cel"
  )) %>% 
  mutate(ecog_at_screening = case_when(
    race == 1             ~ "NHW",
    race == 2             ~ "NHB",
    race == 3             ~ "Hipanic",
    race == 4             ~ "Asian",
    race == 5             ~ "Others"
  )) %>% 
  mutate(myeloma_sub_type = case_when(
    myeloma_sub_type == 1             ~ "IgG",
    myeloma_sub_type == 2             ~ "IgA",
    myeloma_sub_type == 3             ~ "IgD",
    myeloma_sub_type == 4             ~ "IgM",
    myeloma_sub_type == 5             ~ "lc"
  )) %>% 
  mutate(light_chain_subtype = case_when(
    light_chain_subtype == 1             ~ "kappa",
    light_chain_subtype == 0             ~ "lambda"
  )) %>% 
  mutate(deletion_17p_prior_to_car_t_infusion_1_0 = case_when(
    deletion_17p_prior_to_car_t_infusion_1_0 == 1             ~ "Yes",
    deletion_17p_prior_to_car_t_infusion_1_0 == 0             ~ "No"
  )) %>% 
  mutate(t_4_14_prior_to_car_t_infusion_1_0 = case_when(
    t_4_14_prior_to_car_t_infusion_1_0 == 1             ~ "Yes",
    t_4_14_prior_to_car_t_infusion_1_0 == 0             ~ "No"
  )) %>% 
  mutate(t_14_16_prior_to_car_t_infusion_1_0 = case_when(
    t_14_16_prior_to_car_t_infusion_1_0 == 1             ~ "Yes",
    t_14_16_prior_to_car_t_infusion_1_0 == 0             ~ "No"
  )) %>% 
  mutate(r_iss_at_car_t_infsion = case_when(
    r_iss_at_car_t_infsion == 1             ~ "I",
    r_iss_at_car_t_infsion == 2             ~ "II",
    r_iss_at_car_t_infsion == 3             ~ "III"
  )) %>%
  mutate(prior_auto_sct_1_0 = case_when(
    prior_auto_sct_1_0 == 1             ~ "Yes",
    prior_auto_sct_1_0 == 0             ~ "No"
  )) %>% 
  mutate(amyloid_1_0 = case_when(
    amyloid_1_0 == 1             ~ "Yes",
    amyloid_1_0 == 0             ~ "No"
  )) %>% 
  mutate(plasma_cell_leukemia_1_0 = case_when(
    plasma_cell_leukemia_1_0 == 1             ~ "Yes",
    plasma_cell_leukemia_1_0 == 0             ~ "No"
  )) %>% 
  mutate(extramedullary_disease_1_0 = case_when(
    extramedullary_disease_1_0 == 1             ~ "Yes",
    extramedullary_disease_1_0 == 0             ~ "No"
  )) %>% 
  mutate(disease_status_at_time_of_referral = case_when(
    disease_status_at_time_of_referral == 1             ~ "Refractory/RELAPSED",
    disease_status_at_time_of_referral == 2             ~ "SD",
    disease_status_at_time_of_referral == 3             ~ "PR"
  )) %>%
  mutate(history_of_bleeding_y_n = case_when(
    history_of_bleeding_y_n == 1             ~ "Yes",
    history_of_bleeding_y_n == 0             ~ "No"
  )) %>% 
  mutate(bleeding_event_type = case_when(
    bleeding_event_type == 1             ~ "gross hematuria",
    bleeding_event_type == 2             ~ "SDH",
    bleeding_event_type == 3             ~ "SSI",
    bleeding_event_type == 4             ~ "MSK bleed",
    bleeding_event_type == 5             ~ "GI bleed",
    bleeding_event_type == 6             ~ "Hemptysis"
  )) %>%
  mutate(history_of_clotting_y_n = case_when(
    history_of_clotting_y_n == 1             ~ "Yes",
    history_of_clotting_y_n == 0             ~ "No"
  )) %>% 
  mutate(clotting_event_type = case_when(
    clotting_event_type == 1             ~ "DVT",
    clotting_event_type == 2             ~ "line asso. DVT",
    clotting_event_type == 3             ~ "Thrombotic stroke",
    clotting_event_type == 4             ~ "Portal vein thrombosis",
    clotting_event_type == 5             ~ "Spl. V thrombosis",
    clotting_event_type == 6             ~ "sigmoid sinus thrombus"
  )) %>%
  mutate(neurological_comorbidit_y_pre_car_t_1_0 = case_when(
    neurological_comorbidit_y_pre_car_t_1_0 == 1             ~ "Yes",
    neurological_comorbidit_y_pre_car_t_1_0 == 0             ~ "No"
  )) %>% 
  mutate(vascular_comorbidity_dvt_stroke_ht0_cad_y_0 = case_when(
    vascular_comorbidity_dvt_stroke_ht0_cad_y_0 == 1             ~ "Yes",
    vascular_comorbidity_dvt_stroke_ht0_cad_y_0 == 0             ~ "No"
  )) %>% 
  mutate(anticoagulation_preceding_car_t_y_n = case_when(
    anticoagulation_preceding_car_t_y_n == 1             ~ "Yes",
    anticoagulation_preceding_car_t_y_n == 0             ~ "No"
  )) %>% 
  mutate(event_resulting_in_cessation_of_ac_therapy_y_n = case_when(
    event_resulting_in_cessation_of_ac_therapy_y_n == 1             ~ "Yes",
    event_resulting_in_cessation_of_ac_therapy_y_n == 0             ~ "No"
  )) %>% 
  mutate(bridging_therapy_1_0 = case_when(
    bridging_therapy_1_0 == 1             ~ "Yes",
    bridging_therapy_1_0 == 0             ~ "No"
  )) %>% 
  mutate(bleeding_events_during_or_post_cart_y_n = case_when(
    bleeding_events_during_or_post_cart_y_n == 1             ~ "Yes",
    bleeding_events_during_or_post_cart_y_n == 0             ~ "No"
  )) %>% 
  mutate(bleeding_y_n = case_when(
    bleeding_y_n == 1             ~ "Yes",
    bleeding_y_n == 0             ~ "No"
  )) %>% 
  mutate(who_grade_of_bleeding_259 = case_when(
    who_grade_of_bleeding_259 == 1             ~ "Petechia, purpura, oropharyngeal bleed, epistaxis <1 hr, vaginal bleed <2 pads/dat",
    who_grade_of_bleeding_259 == 2             ~ "Echymosis >10 cms, Hematoma, retinal hemorrhage without vision impairment,hematuria, hemotysis,melena, joint bleed",
    who_grade_of_bleeding_259 == 3             ~ "bleeding req. BT, bleeding with mod hD unstability",
    who_grade_of_bleeding_259 == 4             ~ "severe HD unstability, fata bleeding, CNS bleeding"
  )) %>% 
  mutate(isth_dic_score_5_y_n_at_time_of_event = case_when(
    isth_dic_score_5_y_n_at_time_of_event == 1             ~ "Yes",
    isth_dic_score_5_y_n_at_time_of_event == 0             ~ "No"
  )) %>% 
  mutate(exposure_to_direct_hepatotoxic_drugs_y_n_276 = case_when(
    exposure_to_direct_hepatotoxic_drugs_y_n_276 == 1             ~ "Yes",
    exposure_to_direct_hepatotoxic_drugs_y_n_276 == 2             ~ "No"
  )) %>% 
  mutate(treatment_for_bleeding_event_y_n_277 = case_when(
    treatment_for_bleeding_event_y_n_277 == 1             ~ "Yes",
    treatment_for_bleeding_event_y_n_277 == 2             ~ "No"
  )) %>% 
  mutate(ffp_transfusion_y_n_278 = case_when(
    ffp_transfusion_y_n_278 == 1             ~ "Yes",
    ffp_transfusion_y_n_278 == 2             ~ "No"
  )) %>% 
  mutate(platelet_transfusion_y_n_280 = case_when(
    platelet_transfusion_y_n_280 == 1             ~ "Yes",
    platelet_transfusion_y_n_280 == 2             ~ "No"
  )) %>% 
  mutate(cryoprecipitate_transfusion_y_n_282 = case_when(
    cryoprecipitate_transfusion_y_n_282 == 1             ~ "Yes",
    cryoprecipitate_transfusion_y_n_282 == 2             ~ "No"
  )) %>% 
  mutate(another_site_of_bleeding_if_any = case_when( ############################ Green
    another_site_of_bleeding_if_any == 1             ~ "Yes",
    another_site_of_bleeding_if_any == 2             ~ "No"
  )) %>% 
  
  
  
  
  
  mutate(x3rd_site_of_bleed_y_n = case_when( ################################ PINK
    x3rd_site_of_bleed_y_n == 1             ~ "Yes",
    x3rd_site_of_bleed_y_n == 2             ~ "No"
  )) %>% 
  mutate(treatment_for_thrombosis_y_n_365 = case_when( ######################### ORANGE
    treatment_for_thrombosis_y_n_365 == 1             ~ "Yes",
    treatment_for_thrombosis_y_n_365 == 0             ~ "No"
  )) %>% 
  mutate(tocilizumab_yes_no = case_when(
    tocilizumab_yes_no == 1             ~ "Yes",
    tocilizumab_yes_no == 2             ~ "No"
  )) %>% 
  mutate(steroid_use_yes_no = case_when(
    steroid_use_yes_no == 1             ~ "Yes",
    steroid_use_yes_no == 2             ~ "No"
  )) %>% 
  mutate(anakinra_yes_no = case_when(
    anakinra_yes_no == 1             ~ "Yes",
    anakinra_yes_no == 2             ~ "No"
  )) %>% 
  mutate(any_other_crs_icans_therapy_y_n = case_when(
    any_other_crs_icans_therapy_y_n == 1             ~ "Yes",
    any_other_crs_icans_therapy_y_n == 2             ~ "No"
  )) %>% 
  
  mutate(pod_y_n = case_when(
    pod_y_n == 1             ~ "Yes",
    pod_y_n == 2             ~ "No"
  )) %>% 
  mutate(death_from_clotting_or_bleeding_with_in_90_days_of_car_t = case_when(
    death_from_clotting_or_bleeding_with_in_90_days_of_car_t == 1             ~ "Yes",
    death_from_clotting_or_bleeding_with_in_90_days_of_car_t == 2             ~ "No"
  )) %>%
  # New variable
  # cytogenetics
  mutate(any_cytogenetics = case_when(
    deletion_17p_prior_to_car_t_infusion_1_0 == "YES" | 
      t_4_14_prior_to_car_t_infusion_1_0 == "YES" | 
      t_14_16_prior_to_car_t_infusion_1_0 == "YES"   ~ "YES",
    deletion_17p_prior_to_car_t_infusion_1_0 == "NO" &
      t_4_14_prior_to_car_t_infusion_1_0 == "NO" &
      t_14_16_prior_to_car_t_infusion_1_0 == "NO"    ~ "NO"
  ))
  # mutate(cause = case_when(
  #   c == 1             ~ "Yes",
  #   c == 2             ~ "No"
  # )) %>% 
  # # Remove the < and > sign
  # mutate_at(c("", ""), 
  #           ~ case_when(
  #   str_detect(., "<")                 ~ 0.05,
  #   TRUE                               ~ as.numeric(.)
  # )) %>% 
  # mutate_at(c("", ""), 
  #           ~ case_when(
  #   str_detect(., "<")                 ~ 0.05,
  #   TRUE                               ~ as.numeric(.)
  # ))

```

# Table 1. summarizing the baseline characteristics of the patients reviewed in the study
```{r}
recoded_cart %>% 
  select(
    age, sex,
    platelet_at_time_of_bleeding_event,
    ecog_at_screening,
    r_iss_at_car_t_infsion,
    extramedullary_disease_1_0,
    any_cytogenetics,
    bridging_therapy_1_0,
    prior_auto_sct_1_0,
    refractory_disease_status,
    ldh_at_pre_leukapheresis,
    b2_m_at_pre_leukapheresis,
    marrow_dysplasia_baseline_percent,
    highest_gr_crs_grade_0_5, 
    highest_gr_icans_recorded_relative_to_infusion,
    
    orr_response_at_d_30, orr_response_at_d_90,
    history_of_bleeding_y_n,
    history_of_clotting_y_n,
    neurological_comorbidit_y_pre_car_t_1_0,
    vascular_comorbidity_dvt_stroke_ht0_cad_y_0,
    anticoagulation_preceding_car_t_y_n,
    bleeding_y_n
  ) %>% 
  tbl_summary(by= bleeding_y_n,
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_p() %>% bold_p(t= .05) %>% 
  add_overall() %>% 
  add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Bleeding event**")

recoded_cart %>% 
  select(
    age, sex,
    platelet_at_time_of_bleeding_event,
    ecog_at_screening,
    r_iss_at_car_t_infsion,
    extramedullary_disease_1_0,
    any_cytogenetics,
    bridging_therapy_1_0,
    prior_auto_sct_1_0,
    refractory_disease_status,
    ldh_at_pre_leukapheresis,
    b2_m_at_pre_leukapheresis,
    marrow_dysplasia_baseline_percent,
    highest_gr_crs_grade_0_5, 
    highest_gr_icans_recorded_relative_to_infusion,
    
    orr_response_at_d_30, orr_response_at_d_90,
    history_of_bleeding_y_n,
    history_of_clotting_y_n,
    neurological_comorbidit_y_pre_car_t_1_0,
    vascular_comorbidity_dvt_stroke_ht0_cad_y_0,
    anticoagulation_preceding_car_t_y_n,
    thrombosis_events_post_car_t_y_n
  ) %>% 
  tbl_summary(by= thrombosis_events_post_car_t_y_n,
              statistic = list(all_continuous() ~ "{median} ({min}, {max})"), 
              digits = all_continuous() ~ 1) %>% 
  bold_labels() %>% add_p() %>% bold_p(t= .05) %>% 
  add_stat_label() %>% 
  modify_footnote(update = everything() ~ NA) %>%
  modify_spanning_header(all_stat_cols() ~ "**Thrombosis event**")
```

# Table 2: Types and grades of major CAR-T related toxicities documented among study participants 


# Table 3. showing laboratory findings of patients who received CAR-T cell therapy with frequency of abnormal lab values, and median nadir or peak values as listed in patients with bleeding and thrombosis.


# Figures: 
## 1.	Cumulative incidence

## Figure 2.








